Garbage Collection Evaluation Infrastructure\\ for the Cog VM

### 2018-06-16 paper.tex
added setup and commetns and massage section 2.2

\section{Building Benchmarks}
\label{sec:bench}
\sk{isn't it weird to introduce the built benchmarks without explaining *why* they were chosen? Like, why growing, stable, shrinking is significant regarding garbage collection? same for my 3 benchs, why would I chose those 3 bench strategies? I know it is kind of explained in the result section but maybe it is a bit late}

To build GC benchmarks, we took two approaches. We asked companies for their deployed memory intensive applications and turned them into benchmarks. Multiple benchmarks in this category include closed-source code. In Section \ref{sec:mooseBench}, we describe how we turned a specific application into a benchmark with the help of the company (this specific benchmark does not include closed-source code). Then, to stress the GC on specific aspects, we built a configurable benchmark that based on the configuration emulates heaps with different properties.

@@

Running a new memory management strategy on real-world applications can give a first insight about its performance. Being able to configure a specific set-up, personalized environment, can allow to locally \sk{rephrase} test specific behaviors of the new implementation.
This configurable benchmarking tool has been implemented to emulate specific heap structures and states to potentially trigger edge cases: the user has available a set of twelve options which can be sorted in two categories:

\paragraph{Heap structure.} A first set of options allows the user to modify the heap structure, i.e.\ the amount and sizes of objects to allocate and the possible interactions with these objects. \todo{maybe structure is not actually a good term}

\begin{itemize}
\item \emph{wantedAllocatedSize:} the cumulated size (in Kb) of objects that will be allocated
\item \emph{minSize and maxSize:} the minimum and maximum size of objects
\item \emph{dataObjects, weakStructures, classes, compiledMethods:} the ratio for each of these object types.
\item \emph{accessObjects:} if set to True, access half of the objects allocated on the heap 
\item \emph{readOnly:} if set to False, modify half of the objects allocated on the heap upon accessing  
\end{itemize}

@@

We build three benchmarks out of the potential configurations:
\begin{itemize}
\item \emph{FragmentedHeap:} First, objects are allocated one the heap, and some of them are released, leading to a potential memory fragmentation. Then, new objets with a minimum size greater than the new free chunks sizes are allocated.
\item \emph{LargeObjects:} Only large objets with a size greater than 0xFFFF \sk{put real size in Kb here} are allocated on the heap.
\item \emph{Data0bjects:} The majority of objects that will be allocated on the heap will be Data objects, which only contains integer of a specific size (in this benchmark, one byte)
\end{itemize}

@@

    \begin{subfigure}[b]{.48\textwidth}
	\includegraphics[width=\linewidth]{figures/load} 
	\caption{Load\vspace{0.5cm}}
   	\end{subfigure}\hspace{0.03\textwidth}% 
   	\begin{subfigure}[b]{.48\textwidth}
	\includegraphics[width=\linewidth]{figures/prop} 
	\caption{ExpandProperties\vspace{0.5cm}}
   	\end{subfigure}	
	\begin{subfigure}[b]{.48\textwidth}
	\includegraphics[width=\linewidth]{figures/propCache} 
	\caption{ExpandPropertiesWithCache}
	\end{subfigure\hspace{0.03\textwidth}}%
	   	\begin{subfigure}[b]{.48\textwidth}
	\includegraphics[width=\linewidth]{figures/release} 
	\caption{release}
   	\end{subfigure}

>>>>

\cba{Maybe add vspace here not to have the title bottom of page}

\section{Building Benchmarks}
\label{sec:bench}
\sk{isn't it weird to introduce the built benchmarks without explaining *why* they were chosen? Like, why growing, stable, shrinking is significant regarding garbage collection? same for my 3 benchs, why would I chose those 3 bench strategies? I know it is kind of explained in the result section but maybe it is a bit late}
\cba{Sure, please explain}
To build GC benchmarks, we took two approaches. We asked companies for their deployed memory intensive applications and turned them into benchmarks. Multiple benchmarks in this category include closed-source code. In Section \ref{sec:mooseBench}, we describe how we turned a specific application into a benchmark with the help of the company (this specific benchmark does not include closed-source code). Then, to stress the GC on specific aspects, we built a configurable benchmark that based on the configuration emulates heaps with different properties.

\subsection{Set-up}

To evaluate the performance, we use:
\begin{itemize}
	\item the production VM generated by the CI of opensmalltalk-vm\footnote{https://github.com/OpenSmalltalk/opensmalltalk-vm}, that we call Mark-Compact or Compact.
	\item a custom compiled VM, which features a different compactor, that we call Mark-Sweep or Sweep.
\end{itemize}
We compiled one VMs for Linux with GCC, and one for Mac with LLVM.

\paragraph{Moose benchmark.}The Moose benchmark evaluation was performed on a MacBook pro with Mac OS 10.11.6, a 2.9 Ghz processor Intel Core 5, 8 Gb 1867MHz DDR3 of RAM. The Mac VM was compiled using Apple LLVM version 8.0.0 (clang-800.0.38). The compiled VMs are 64 bits (x64) VMs.

\paragraph{Configurable benchmark.}The Configurable benchmark evaluation was performed on an Asus Zenbook with Ubuntu 16.04 LTS, a 2.2 Ghz processor Intel Core 5, 8 Gb 1600MHz DDR3 of RAM. The Linux VM was compiled using GCC version 5.4.0. The compiled VMs are 32 bits (x86) VMs.

@@

Running a new memory management strategy on real-world applications can give a first insight about its performance. Being able to configure a specific set-up allows to stress specific behaviors of the new implementation.
This configurable benchmarking tool has been implemented to emulate specific heap structures and states to potentially trigger edge cases. The user has available a set of twelve options which can be sorted in two categories:

\paragraph{Heap structure.} A first set of options allows the user to modify the heap structure, i.e.\ the amount and sizes of objects to allocate and the possible interactions with these objects. \todo{maybe structure is not actually a good term} \cba{Heap characteristics? If you change change title and in previous paragraph}

\begin{itemize}
\item \emph{wantedAllocatedSize:} the cumulated size (in Kb) of objects that will be allocated.
\item \emph{minSize and maxSize:} the minimum and maximum size of objects.
\item \emph{dataObjects, weakStructures, classes, compiledMethods:} the ratio for each of these object types. \cba{Ephemerons}
\item \emph{accessObjects:} if set to True, access half of the objects allocated on the heap .
\item \emph{readOnly:} if set to False, modify half of the objects allocated on the heap upon accessing.
\end{itemize}

@@

We build three benchmarks out of the potential configurations:
\begin{itemize}
\item \emph{FragmentedHeap:} First, objects are allocated on the heap, and some of them are released, leading to a potential memory fragmentation. Then, new objets with a minimum size greater than the new free chunks sizes are allocated.
\item \emph{LargeObjects:} Only large objets with a size greater than 0xFFFF \sk{put real size in Kb here} are allocated on the heap.
\item \emph{Data0bjects:} The majority of objects that will be allocated on the heap will be Data objects, which only contains integer of a specific size (in this benchmark, one byte) \cba{I would not say they hold integer. Data objects can theoretically hold float/double for example, of an int used as a bitmap}
\end{itemize}

@@

    \begin{subfigure}[b]{.48\textwidth}
	\includegraphics[width=\linewidth]{figures/load} 
	\caption{Load\vspace{0.5cm}}
   	\end{subfigure}\hspace{0.03\textwidth}% 
   	\begin{subfigure}[b]{.48\textwidth}
	\includegraphics[width=\linewidth]{figures/prop} 
	\caption{ExpandProperties\vspace{0.5cm}}
   	\end{subfigure}	
	\begin{subfigure}[b]{.48\textwidth}
	\includegraphics[width=\linewidth]{figures/propCache} 
	\caption{ExpandPropertiesWithCache}
	\end{subfigure}\hspace{0.03\textwidth}%
	   	\begin{subfigure}[b]{.48\textwidth}
	\includegraphics[width=\linewidth]{figures/release} 
	\caption{release}
   	\end{subfigure}
